{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-08-17 paper/tex/sections/results.tex
add snr plot

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig5_snr_cumulative_all.pdf}
    \caption{Cumulative number of LISA detections with a given signal-to-noise ratio. Colours indicate LISA mission length and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:snr_dist}
\end{figure}
